\clearpage
\section{Magic Flan Cake}

\index{author!Heather Baird}
\index{cake}
\index{flan}
\index{chocolate}
  
Source: https://www.sprinklebakes.com/2014/06/magic-flan-cake.html

  \begin{multicols}{2}
    \subsection{Ingredients - Cake}
      \begin{itemize}
        \item \sfrac{1}{2} cup prepared caramel sauce
        \item 60g + 2 tbsp plain flour
        \item 46g cup cocoa powder
        \item 2 tsp cinnamon
        \item \sfrac{1}{2} tsp baking soda
        \item \sfrac{1}{4} tsp salt
        \item 115g bittersweet chocolate, chopped
        \item 85g unsalted butter
        \item \sfrac{1}{2} cup buttermilk
        \item 105g sugar
        \item 2 large eggs
        \item 1 tsp vanilla extract
      \end{itemize}
      \subsection{Ingredients - Flan}
        \begin{itemize}
          \item 2 cans (400g each) sweetened condensed milk
          \item 2\sfrac{1}{2} cups whole milk, room temperature
          \item 170g cream cheese, room temperature
          \item 6 large eggs, room temperature
          \item 4 large egg yolks, room temperature
          \item 1 tsp vanilla extract
        \end{itemize}
  \vfill\null
  \columnbreak
  \subsection{Method}
    \begin{enumerate}
      \item Preheat the oven to \ang{175}C. Grease a 12-cup bundt tin.
      \item Pour the caramel sauce event into the bottom of the pan.
      \item In a bowl, combine the flour, cocoa, cinnamon, baking soda, and salt. Set aside.
      \item Combine chocolate and butter in a microwave-safe bowl and heat at 30 second increments, stirring between heating until smooth.
      \item Add the buttermilk, sugar, eggs, and vanilla to the chocolate mixture and whisk until incorporated.
      \item Add the flour mixture and stir until combined.
      \item Pour the chocolate batter over the caramel in the baking tin.
      \item Add all the flan ingredients to a blender and process on high until smooth.
      \item Slowly pour the flan mixture over the cake batter.
      \item Place the pan in a large roasting pan, and place in the oven. Fill the roasting pan with hot water until it reaches half the height of the bundt tin.
      \item Back for 80 to 90 minutes or until a toothpick comes out with a few moist crumbs.
      \item Place bundt tin on a cooling rack and allow to cool completely, before moving to a refrigerator for 8 hours (or overnight).
    \end{enumerate}
    To unmold the cake, fill a large bowl (or your sink) with hot water. Place the bottom of the cake pan in the water to warm the caramel/flan portion of the cake. This will help the cake release. Turn the cake out onto a large serving platter or a cake stand that has a lip. The caramel will drizzle down over the cake as you remove the pan. Store the cake covered in plastic wrap in the refrigerator.
  \end{multicols}
