\clearpage
\section{Beef Casserole with Cheesy Potato Dumplings}

\index{meat!beef}
\index{meat!beef!round}
\index{starch!potato}
\index{stew}
\index{casserole}

\subsection{Ingredients}

Casserole:

\begin{itemize}
    \item 1kg beef round
    \item 2-3 Onions, roughly chopped
    \item 4 rashers bacon, roughly chopped
    \item 2 cloves garlic, crushed
    \item 300g mushrooms, chopped unless button variety
    \item 400g can crushed tomatoes
    \item 1\sfrac{1}{2} cups beef stock
    \item \sfrac{1}{4} cup tomato paste
    \item \sfrac{1}{3} cup red wine vinegar
\end{itemize}

Dumplings:

\begin{itemize}
    \item 2 large potatoes
    \item \sfrac{3}{4} cup milk
    \item 60g butter
    \item 1\sfrac{1}{2} cups self-raising flour
    \item \sfrac{3}{4} cup grated cheddar
    \item \sfrac{1}{2} cup grated parmesan
    \item pinch of salt
\end{itemize}

\subsection{Method}

\begin{enumerate}
    \item Brown meat in batches over high heat.
    \item Cook onion, bacon, garlic over medium heat until bacon is crisp.
    \item Add all other casserole ingredients to pot and simmer for 1\sfrac{1}{2}-2 hours.
    \item Meanwhile, boil potatoes until tender.
    \item Mash with milk and butter until smooth.
    \item Stir in flour, chedder, parmesan. Salt as required.
    \item Shape dumplings into rough balls, place on oven tray.
    \item Bake at \celsius{180} until golden brown on top, then flip them and repeat for the other side.
    \item When the dumplings are cooked, add them to the casserole for the last 20-30 minutes.
\end{enumerate}
