\section{Boeuf Bourguignon}

\index{meat!beef}
\index{meat!beef!steak}
\index{alcohol!brandy}
\index{alcohol!red wine}
\index{stew}
\index{starch!potato}

  \begin{multicols}{2}
    \subsection{Ingredients}
      \begin{itemize}[noitemsep]
        \item 1 large onion, thinly sliced
        \item 1 sprig parsley
        \item Large pinch dried thyme
        \item 1 bay leaf, crushed
        \item 1kg steak, cubed
        \item 2 tbsp brandy
        \item 400mL red wine
        \item 2 tbsp olive oil
        \item 50g butter
        \item 150g lean bacon, julienned
        \item 24 small pickling onions
        \item 450g button mushrooms, sliced
        \item 25g plain flour
        \item 300mL beef stock
        \item 1 clove garlic, crushed
        \item 1 bouquet garni
        \item Salt and pepper
        \item 4-6 potatoes (for serving, see below)
        \item Butter for potatoes
        \item Parsley for potatoes
      \end{itemize}

      Serve with potatoes tossed in melted butter and parsley.

      \subsection{Variations}
        \subsubsection{Pie}
          After adding the bacon, onion, and mushrooms, simmer for 10 minutes less (20 minutes total), then transfer to a pie dish (optionally, line with pastry first). Put pastry over the top and bake in a moderate oven until pastry is cooked.

      \vfill\null
    \columnbreak
    \subsection{Method}
      \begin{enumerate}
        \item Put large onion, parsley, thyme, bay leaf, brandy, red wine, steak, and olive oil in a large bowl or container.
        \item Leave for 4 hours, stirring occasionally.
        \item Melt butter in a cast iron pot (dutch oven or similar). Add bacon and fry over medium heat until browned. Remove to a bowl.
        \item Put the small onions into the pan (add more butter if necessary) and fry until lightly browned on all sides. Remove to bacon bowl.
        \item Put mushrooms in pan (again, more butter if needed) and fry for a minute, then remove to the bacon bowl.
        \item Cover the bacon bowl and set aside for now.
        \item Remove beef pieces from marinade, then strain marinade and set aside.
        \item Dry the beef with paper towels.
        \item Put beef in pot (again, more butter) and brown.
        \item Sprinkle flour over and cook, stirring, for 1 minute.
        \item Stir in the marinade gradually, then add the stock, garlic, and bouquet garni. Add salt and pepper to taste.
        \item Cover, then simmer gently for at least 2 hours.
        \item Add the bacon, onions, and mushrooms, then cover and simmer for 30 minutes.
        \item Discard the bouquet garni, taste, and adjust seasoning if needed.
      \end{enumerate}
    \end{multicols}
