\section{Caramelized Pork Tacos with Pineapple Salsa}

\index{author!Lindsay Mostrom}
\index{source!pinchofyum.com}
\index{meat!pork}
\index{meat!pork!loin}
\index{starch!bread}
\index{country!Mexico}

Source: https://pinchofyum.com/caramelized-pork-tacos-with-pineapple-salsa

\subsection{Ingredients}

\begin{multicols}{2}
    For the pork

    \begin{itemize}
        \item 1 shallot, minced
        \item 1 clove garlic, minced
        \item 1 jalapeño, diced with ribs and seeds removed
        \item 2 tsp fish sauce
        \item 500g boneless pork loin, sliced into thin strips
        \item 2 tbsp sugar
        \item 2 tbsp water
    \end{itemize}

    \vfill\null
    \columnbreak

    For the pineapple salsa

    \begin{itemize}
        \item 1 cup pineapple, finely diced
        \item 1 cup cucumber, finely diced
        \item \sfrac{1}{2} cup cilantro, roughly minced
        \item \sfrac{1}{2} red onion or shallot, finely diced
        \item a squeeze of lime juice
    \end{itemize}

    For serving

    \begin{itemize}
        \item 8 tortillas
        \item \sfrac{1}{4} cup cilantro
        \item 1 lime, sliced into sections
        \item Sriracha mayo (\sfrac{1}{4} cup mayo and 2 tsp Sriracha)
    \end{itemize}
\end{multicols}

\subsection{Method}

\begin{enumerate}
    \item Heat the oil in a heavy pan over medium heat. Add the shallot, garlic, and jalapeño, and saute until fragrant, about 2 minutes. Turn the heat to high and add the pork and the fish sauce. Stir fry for a few minutes until the pork is no longer pink. With the heat very high, add the sugar and water and stir once, then let the pork caramelize by not stirring it for about 1 minute. Repeat this process until the pork is nice and golden brown.
    \item Toss all the salsa ingredients together in a bowl.
    \item Warm the tortillas quickly in a skillet with a little bit of oil. Divide the pork between the tortillas and top with the salsa and the mayo.
\end{enumerate}
