\section{Channa Masala / \emph{Chickpea curry}}

\index{author!J. Kenji Lopez-Alt}
\index{source!seriouseats.com}
\index{vegetarian}
\index{starch!rice}
\index{starch!bread}
\index{country!India}

Source: https://www.seriouseats.com/channa-masala-recipe

\subsection{Ingredients}

\begin{itemize}
    \item 4 cloves garlic, roughly chopped
    \item 1" knob ginger, peeled, roughly chopped
    \item 1-6 green Thai chiles (to taste), roughly chopped
    \item 2 tbsp juice from 1 lemon, divided
    \item 2 tbsp vegetable oil or ghee
    \item 2 tsp black mustard seeds
    \item 1 tsp whole cumin seeds
    \item 1 large onion, finely diced
    \item \sfrac{1}{4} tsp baking soda
    \item 2 tsp ground coriander
    \item \sfrac{1}{2} tsp freshly ground black pepper
    \item \sfrac{1}{2} tsp ground turmeric
    \item 1\sfrac{1}{2} tsp garam masala, divided
    \item 1 400g can whole peeled tomatoes
    \item 2 400g cans chickpeas, drained and rinsed
    \item 1 cup coriander leaves, roughly chopped
\end{itemize}

\subsection{Method}

\begin{enumerate}
    \item Combine garlic, ginger, chiles, 1 tbsp lemon juice, and \sfrac{1}{2} tsp kosher salt in a mortar and pestle or in the small work bowl of a food processor and pound or process until a fine paste is produced. Set aside.
    \item Heat oil or ghee in a large saucepan or Dutch oven over medium-high heat until shimmering. All at once, add mustard seeds and cumin. They will sputter and spit for a few seconds. As soon as they are aromatic (about 15 seconds), add onion all at once, along with baking soda. Cook, stirring frequently, until onions start to leave a brown coating on bottom of pan, 3 to 4 minutes. Add 1 tbsp water, scrape up browned bits from pan, and continue cooking. Repeat this process until onions are a deep brown, about 10 minutes total.
    \item Immediately add garlic/ginger/chile paste all at once and stir to combine. Add ground coriander, black pepper, turmeric, and 1 tsp garam masala. Stir until fragrant, about 30 seconds. Add tomatoes and crush them using a whisk or potato masher. Add chickpeas and coriander leaves, reserving a little coriander for garnish. Add \sfrac{1}{2} cup water.
    \item Bring to a simmer, cover with lid slightly cracked, and reduce heat to maintain a gentle bubbling. Cook, stirring occasionally, until liquid has reduced into a thick stew and spices have melded, about 30 minutes.
    \item Stir in remaining garam masala and lemon juice. Season to taste with salt. Serve with rice and/or naan, sprinkling additional coriander on top.
\end{enumerate}

