\section{Chickpea, Coconut, and Cashew Curry}

\index{author!J. Kenji Lopez-Alt}
\index{source!seriouseats.com}
\index{vegetarian}
\index{starch!rice}
\index{starch!bread}
\index{country!India}
\index{quick-n-easy}

Source: https://www.seriouseats.com/braised-eggplant-with-tofu-in-garlic-sauce-recipe

\subsection{Ingredients}

\begin{itemize}
    \item 3 tablespoons vegetable oil, butter, or ghee
    \item 1 small onion, finely minced
    \item 4 cloves garlic, minced
    \item 1 tbsp fresh ginger, minced
    \item 1 small red or green chilli, finely chopped
    \item \sfrac{1}{4} tsp cayenne pepper
    \item \sfrac{1}{2} cup cashew nuts
    \item 1 400g can coconut milk
    \item 2 400g cans chickpeas, drained and rinsed
    \item 1 bunch flat spinach leaves, and roughly chopped
    \item \sfrac{1}{4} cup fresh lime juice (3-4 limes)
    \item \sfrac{1}{2} cup fresh coriander, coarsely chopped
\end{itemize}

\subsection{Method}

\begin{enumerate}
    \item Combine cumin, coriander, star anise, cloves, peppercorns, cinnamon, nutmeg, mace, turmeric, and cardamom in a spice grinder and grind to a fine powder. Set aside.
    \item Heat oil, butter, or ghee in a large saucepan over medium-high heat until melted (or until oil is shimmering). Add onion, garlic, ginger, and chile. Cook, stirring frequently, and scraping bottom of pan until golden brown and starting to burn in spots, about 10 minutes. Add cayenne, cashews, and half of spice mixture. Cook, stirring constantly until fragrant, about 30 seconds. Add coconut milk and remove from heat. Scrape up any browned bits from bottom of pan.
    \item Transfer mixture to blender and starting a low speed, slowly increase speed to maximum. Blend until smooth, about 30 seconds. Return mixture to pot. Add chickpeas, spinach, and remaining spice mix and cook over low heat, stirring constantly, until vegetables are heated through and spinach is wilted, about 10 minutes. Add salt and lime juice to taste. Stir in half of cilantro.
    \item Transfer to serving bowl, sprinkle with extra cilantro, and serve with lime wedges, basmati rice pilaf, grilled naan, and cilantro chutney, as desired.

\end{enumerate}
