\section{Creamy Tomato and Bean Soup}

\index{author!Nagi Maehashi}
\index{source!recipetineats.com}
\index{vegetarian}

Source: https://www.recipetineats.com/creamy-tomato-bean-soup

\subsection{Ingredients}

\begin{itemize}
    \item 2 tbsp unsalted butter
    \item 1 onion, finely chopped
    \item 2 cloves garlic, minced
    \item 1 carrot , large, peeled and finely diced
    \item 1\sfrac{1}{2} tsp Italian herb mix
    \item \sfrac{3}{4} cup tomato paste
    \item \sfrac{1}{2} cup dry white wine
    \item 4 cups vegetable stock
    \item 3 400g cans cannellini or any white beans, rinsed and drained
    \item \sfrac{1}{2} cup parmesan, grated
    \item 120g baby spinach
    \item \sfrac{3}{4} cup heavy cream
\end{itemize}

\subsection{Method}

\begin{enumerate}
    \item Melt butter in a pot over medium high heat. Cook garlic, onion and carrot for 5 minutes until carrot is soft and sweet.
    \item About 3 minutes in, add the Italian herbs and cook with the onion (makes the herb flavour "bloom").
    \item Turn heat up to high, add tomato paste. Cook for 2 minutes to remove the "raw" flavour.
    \item Add white wine, cook for 3 minutes until the harsh "winey" smell is gone and mostly evaporates so you're just left with tomato paste again.
    \item Add \sfrac{1}{2} cup of beans to thicken soup, stock, parmesan, salt, and pepper. Stir, low heat, cover and simmer 3 minutes, stirring every now and then.
    \item Use a stick blender to puree until smooth.
    \item Add remaining beans, simmer 3 minutes. Stir in spinach until wilted, then stir in cream if using. Season to taste.
    \item Serve with crusty bread for dunking!
\end{enumerate}
