\section{Moroccan Egg Drop Harira}

\index{author!Nargisse Benkabbou}
\index{source!seriouseats.com}
\index{vegetarian}
\index{starch!rice}
\index{country!Morocco}

Source: https://www.seriouseats.com/moroccan-egg-drop-harira-recipe-7109917

\subsection{Ingredients}

\begin{itemize}
    \item 1\sfrac{1}{2} tbsp extra-virgin olive oil
    \item 1 tbsp ghee or unsalted butter
    \item 1 medium yellow onion, finely chopped
    \item 1 cup celery, finely chopped
    \item 1\sfrac{1}{2} cups tomato passata
    \item \sfrac{1}{4} cup flat-leaf parsley (leaves and tender stems), finely chopped
    \item 2 tsp ground ginger
    \item 1\sfrac{1}{4} tsp salt
    \item 1 tsp ground turmeric
    \item \sfrac{1}{2} tsp freshly ground black pepper
    \item \sfrac{1}{4} tsp ground cinnamon
    \item \sfrac{1}{8} tsp saffron threads
    \item 5 cups vegetable stock (low sodium)
    \item \sfrac{1}{3} cup dried green lentils
    \item \sfrac{1}{4} cup long-grain white rice, uncooked
    \item \sfrac{1}{2} cup canned chickpeas, rinsed and drained
    \item 1 tbsp cornstarch
    \item 1 large egg, lightly beaten
    \item 2 tbsp fresh coriander (leaves and tender stems), finely chopped
    \item Coriander leaves, for serving
    \item Lemon wedges, for serving
\end{itemize}

\subsection{Method}

\begin{enumerate}
    \item In a large pot, heat olive oil and butter over medium heat until butter is foamy. Add onions and celery and cook, stirring occasionally, until the onions start to soften, 5 to 6 minutes.
    \item Stir in passata, parsley, ground ginger, salt, ground turmeric, black pepper, cinnamon, and saffron. Cook, stirring often, until fragrant, about 1 minute.  Stir in vegetable broth and bring to a boil over high heat. Cover pot, reduce heat to low, and simmer for 1 hour.
    \item Stir in lentils and rice, cover pot, and cook for 5 minutes. Stir in chickpeas, cover, and cook until both the rice and lentils are almost cooked, about 10 minutes longer.
    \item In a small bowl, whisk together cornstarch and with 1 tbsp water until smooth. Add to the soup and stir well to combine. Increase heat to medium and simmer, uncovered, stirring occasionally, until the harira thickens and lentils are tender, 5 to 8 minutes.
    \item While stirring the soup in a circular motion using a ladle, slowly pour the beaten egg in to form threads, then simmer harira for 1 minute until the eggs are fully cooked. Season with salt, if desired.
    \item Stir in chopped cilantro and serve immediately with lemon wedges and more cilantro leaves.
\end{enumerate}

