\clearpage
\section{Kaddo Bourani / \emph{Afghan Pumpkin with Yoghurt and Meat}}

\index{meat!beef}
\index{meat!beef!mince}
\index{country!Afghanistan}
\index{source!goonswithspoons.com}

From \detokenize{http://goonswithspoons.com/Kaddo_Bowrani}

\subsection{Ingredients}

Pumpkin

\begin{itemize}
	\item 1 (~1.5kg) pumpkin, peeled and cut into 2" cubes
	\item \sfrac{1}{3} cup sugar
	\item \sfrac{3}{4} tsp ground cinnamon
	\item 2 tbsp oil
\end{itemize}

Yoghurt Sauce

\begin{itemize}
	\item 1\sfrac{1}{2} cups Greek yoghurt
	\item 2 cloves garlic, crushed
	\item \sfrac{3}{4} tsp dried mint
\end{itemize}

Meat Sauce

\begin{itemize}
    \item 1kg beef mince
    \item 2 medium onions, diced
    \item 2 tomato, finely chopped
    \item 2 clove garlic, crushed
    \item 2 tbsp tomato paste
    \item 1 tsp turmeric
    \item 2 tsp ground coriander
    \item 1 cup water
\end{itemize}

You could also add other vegetables, such as carrot, turnip, or zucchini, to the meat sauce.

\subsection{Method}

\begin{enumerate}
    \item Heat oil in a large pan and brown the pumpkin pieces, turning often to avoid burning.
    \item Sprinkle with sugar and cinnamon, stir, and bake in a \celsius{180} oven until tender (~30 minutes).
    \item Mix yoghurt sauce ingredients together, season to taste, and refrigerate until needed.
    \item In a pan, heat 2 tbsp of oil and lightly brown the onions.
    \item Add the meat and garlic, and season with salt and pepper. Mix well and cook until the beef is nicely browned.
    \item Add tomato, tomato paste, and spices. Bring to a boil, then reduce heat and simmer for 5 minutes.
    \item To serve, plate the meat sauce, top with pieces of pumpkin, and drizzle with the yoghurt sauce.
\end{enumerate}
