\section{Kare Raisu / \emph{Japanese Curry}}

\index{starch!rice}
\index{meat!chicken}
\index{meat!chicken!breast}
\index{country!Japan}
\index{author!J. Kenji Lopez-Alt}
\index{curry!Japanese}

From https://www.youtube.com/watch?v=QhsrBz9Cceg.

\subsection{Ingredients}

\begin{itemize}
	\item 4 tablespoons clarified butter or oil
	\item 500g chicken breast
	\item \sfrac{1}{2} a large yellow onion
	\item 3-4 cloves garlic, minced
	\item 1" knob fresh ginger, minced
	\item 3 tbsp Japanese curry powder, such as S and B
	\item 4 tbsp flour
	\item 4 cups chicken stock
	\item 1 large Yukon gold potato, peeled
	\item 1 large carrot, peeled
	\item 1 tbsp honey
	\item \sfrac{1}{2} cup raisins
	\item 1 cup frozen green peas
\end{itemize}

The meat and all vegetables should get a 1\sfrac{1}{2}" dice (slices, for the onion).

\subsection{Method}

\begin{enumerate}
	\item Heat the butter over high heat until lightly smoking. Reduce heat to medium-high. Add the chicken and cook, stirring occasionally, until lightly browned, about 3 minutes. Add the onions, season with salt and pepper, and cook, stirring, until the onions are softened, about 3 minutes.
	\item Add the garlic and ginger and cook, stirring, until aromatic, about 30 seconds. Add the curry powder and cook, stirring, until lightly toasted, about 30 seconds.
	\item Add the flour and cook, stirring, until no pockets of dry flour remain, about 30 seconds. Add the broth or water and stir to dissolve the flour. Add  the potatoes, carrots, honey, and raisins. Bring to a simmer, then reduce heat to maintain a bare simmer. Cover and cook until the potatoes and carrots are tender but not falling apart, about 10 minutes.
	\item Season  to taste with salt, pepper, and more honey if desired. Stir in the peas. Serve with steamed white rice, thinly sliced Chinese chives or scallions, and Japanese pickles.
\end{enumerate}
