\section{Kenji's 15-Minute Chili}

\index{meat!beef}
\index{meat!beef!mince}
\index{country!USA}
\index{author!J. Kenji Lopez-Alt}

Adapted from The Food Lab


Sometimes even the best of us don’t feel like going all out. Here’s a much quicker weeknight chili that uses a few of the tricks learned from my Best Short-Rib Chili and the 30-minute bean soup recipes. I use ground beef here, which precludes real browning as an option, but a couple of smoky chipotle chiles added to the mix lend a similar sort of deep complexity. Serve the chili with grated cheddar cheese, sour cream, chopped onions, scallions, sliced jalapeños, diced avocado, and/or chopped cilantro, along with corn chips or warmed tortillas.

\subsection{Ingredients}

\begin{itemize}
	\item 4 tablespoons unsalted butter
	\item 2 medium onions, grated on the large holes of a box grater
	\item 2 large cloves garlic, minced
	\item 1 tsp dried oregano
	\item Salt
	\item 2 chipotle chiles packed in adobo, finely chopped
	\item 2 anchovy fillets, mashed to a paste with the back of a fork
	\item \sfrac{1}{2} cup Chile Paste or 1⁄4 cup chili powder
	\item 1 tbsp ground cumin
	\item \sfrac{1}{2} cup tomato paste
	\item 1kg beef mince
	\item 800g can whole tomatoes, drained and chopped into half-inch pieces
	\item 400g can red kidney beans, drained
	\item 1 cup homemade or low-sodium canned chicken stock, or water
	\item 2-3 tablespoons instant cornmeal (such as Maseca)
	\item 2 tbsp whiskey, vodka, or brandy (optional)
	\item Freshly ground black pepper
	\item Garnishes as desired (see the headnote) 
\end{itemize}

\subsection{Method}

\begin{enumerate}
	\item Melt the butter in a large Dutch oven over medium-high heat. Add the onions, garlic, oregano, and a pinch of salt and cook, stirring frequently until the onions are light golden brown, about 5 minutes. Add the chipotles, anchovies, chile paste, and cumin and cook, stirring, until aromatic, about 1 minute. Add the tomato paste and cook, stirring until homogeneous, about 1 minute.
	\item Add the ground beef and cook, using a wooden spoon to break up the beef into pieces and stirring frequently, until no longer pink (do not try to brown the beef), about 5 minutes. Add the tomatoes, beans, stock, and cornmeal and stir to combine. Bring to a boil, reduce to a simmer, and cook, stirring occasionally, until the flavors have developed and the chili is thickened, about 30 minutes.
	\item Stir in the whiskey, if using. Serve with some or all of the suggested garnishes, along with corn chips or tortillas.
\end{enumerate}
