\section{Khoresh-é-Bādemjan / \emph{Persian meat and eggplant stew}}

\index{starch!rice}
\index{meat!lamb}
\index{meat!lamb!shoulder}
\index{author!Nader Mehravari}
\index{source!seriouseats.com}
\index{country!Iran}

Sources: https://www.seriouseats.com/khoresh-e-bademjan-persian-meat-and-eggplant-stew-recipe-8422715

\subsection{Ingredients}

\begin{itemize}
    \item 900g eggplant, trimmed, peeled, and cut into 1" discs
    \item 500g boneless leg of lamb, shoulder, 1\sfrac{1}{2}" cubed
    \item \sfrac{1}{2} tsp salt
    \item \sfrac{1}{2} tsp black pepper, freshly ground
    \item 1 small onion, diced medium-chunky
    \item 1 tsp ground turmeric
    \item 3 tbsp tomato paste
    \item 1 tbsp fresh lemon juice
    \item 1 tomato, cored and cut into 3 round slices (optional)
\end{itemize}

\subsection{Method}

\begin{enumerate}
    \item Set a wire rack in a rimmed baking sheet and line with a triple layer of paper towels. Fill a 12" pan \sfrac{1}{4}" deep with oil, then heat over medium-high heat until oil is shimmering but not smoking. Fry eggplant slices, flipping once halfway through, until dark golden brown on both sides, about 10 minutes. Transfer eggplant to prepared wire rack. Set cooked eggplant aside.
    \item In a large pot, heat oil over medium-high heat until shimmering. Season meat evenly with salt and pepper and add to the saucepan in a single layer. Cook, turning occasionally, until meat is well browned on all sides, about 10 minutes. With a slotted spoon, transfer meat to a plate and set aside.
    \item Heat remaining fat in the Dutch oven over medium heat until shimmering, and add onion. Cook until the onion is softened and golden brown, 5-7 minutes.
    \item Stir in turmeric and cook until aromatic, 30 seconds. Stir in tomato paste and cook until well incorporated and beings to darken in color, 1 minute longer.
    \item Add 2 cups water and bring to a boil over medium-high heat. Scrape the bottom to free up any stuck brown bits. Stir in the meat and return to a boil, then cover, reduce heat to medium-low, and cook for 10 minutes.
    \item Remove the lid and give the contents a gentle stir. Adjust the heat as needed to maintain a gentle simmer. Cover and cook for 30 minutes. Stir in lemon juice.
    \item Gently arrange the eggplant halves on top of the meat in an even layer, overlapping if needed. Using a spatula, gently press down on the eggplant and carefully shake the pot in a swirling motion to submerge the eggplant into the braising liquid (you don't want to break the eggplant pieces by stirring them in). Cover and continue cooking at a gentle simmer for 30 minutes longer, swirling the pot every 10 minutes.
    \item (optional) Meanwhile, in a small skillet, heat 1 1/2 teaspoons oil over medium heat until shimmering, then cook the tomato slices until limp, about 5 minutes.
    \item Season with additional salt or lemon juice, if desired (Persian dishes are often more sour than salty, though feel free to follow your personal preferences). Gently transfer the finished braise to a serving dish. Rather than spooning it in, which can break up the eggplant too much, tip the pot carefully over the edge of the serving dish so that the contents can slowly slide into it. Garnish with tomato slices and serve with rice.
\end{enumerate}