\section{Labaniyeh bil Ruz / \emph{Garlicky Yogurt and Rice Porridge}}

\index{author!Reem Kassis}
\index{source!seriouseats.com}
\index{starch!rice}
\index{vegetarian}
\index{country!Italy}

Source: https://www.seriouseats.com/labaniyeh-bil-ruz-5180234

\subsection{Ingredients}

\begin{itemize}
    \item 450g full-fat plain or Greek yogurt 
    \item 1 tsp cornstarch
    \item 1 tbsp extra-virgin olive oil
    \item 4 cloves garlic, minced
    \item 1 tsp fresh lemon juice
    \item 310g cooked plain medium- or short-grain white rice
    \item \sfrac{1}{4} cup toasted or fried pine nuts or slivered almonds, for garnish
    \item Crushed dried mint, for garnish
\end{itemize}

Adding meat or vegetables sounds like a delicious option.

\subsection{Method}

\begin{enumerate}
    \item In a 3-4L stainless-steel saucepan or enameled Dutch oven, combine yogurt, 2 cups water, and cornstarch and bring to a boil over medium-high heat, whisking constantly to prevent curdling (you do not want the yogurt to break into curds, so constant whisking until it boils is absolutely essential). Reduce heat to a bare simmer, whisking occasionally to prevent scorching. Season with salt.
    \item While the yogurt simmers, combine olive oil and garlic in a small skillet and set over medium heat. Cook, stirring and swirling the skillet often, until garlic is fragrant but not browned, 1 to 2 minutes.
    \item Pour the garlic and its oil into the yogurt and stir. The sauce should be quite sour, but will vary based on the yogurt used; add optional lemon juice, if needed.
    \item Stir rice into the yogurt until well combined; season with salt, if needed. Increase heat slightly and bring to a simmer, then cook, stirring often, until you reach a porridge-like consistency similar to a thin risotto or rice pudding, about 15 minutes; you may need to add more water depending on the rice you are using, but keep in mind that the consistency will also thicken as it cools.
    \item To serve, ladle the rice into shallow bowls and, if using, top with the toasted nuts and/or dried mint.
\end{enumerate}
