\section{Lamb Korma / \emph{Lamb with spices and yoghurt}}

\index{starch!rice}
\index{meat!lamb}
\index{meat!lamb!leg}
\index{author!Charmaine Solomon}
\index{country!India}
\index{curry!Indian}

From: Charmaine Solomon's Complete Asian Cookbook

Serves: 6

\subsection{Ingredients}

\begin{itemize}
	\item 1kg boned leg of lamb
	\item 2 onions
	\item 1 tbsp finely chopped fresh ginger 
	\item 2 large garlic cloves 
	\item 40g raw cashew nuts or blanched almonds 
	\item 2–6 dried red chillies, deseeded 
	\item 2 tsp ground coriander 
	\item 1 tsp ground cumin 
	\item \sfrac{1}{4} tsp ground cinnamon 
	\item \sfrac{1}{4} tsp ground cardamom 
	\item \sfrac{1}{4} tsp ground cloves 
	\item \sfrac{1}{2} tsp saffron strands 
	\item 2 tbsp boiling water 
	\item 20g ghee 
	\item 2 tbsp oil 
	\item 2 tsp salt 
	\item \sfrac{1}{2} cup plain yoghurt 
	\item 2 tbsp chopped fresh coriander
\end{itemize}

\subsection{Method}

\begin{enumerate}
	\item Cut the lamb into large cubes, trimming off any excess fat.
	\item Peel the onions; slice one thinly and set aside. Finely chop the other onion and place in a food processor with the ginger, garlic, cashew nuts and chillies. Add \sfrac{1}{2} cup water and process to make a smooth paste. Add all the ground spices and process until well combined. 
	\item Put the saffron strands into a small bowl with the boiling water and allow to soak while cooking the masala. 
	\item Heat the ghee and oil in a large saucepan over low heat. Add the sliced onion and cook, stirring frequently with a wooden spoon, until soft and golden. Add the spice mixture and continue to cook, stirring constantly until the oil starts to separate. Add \sfrac{1}{4} cup water to the pan together with the salt and continue to stir until the liquid evaporates. Add the lamb and stir over medium heat until each piece is coated with the spice. Stir the saffron, crushing the strands against the side of the bowl, then add to the pan and stir to combine. Add the yoghurt and stir again until mixed through. 
	\item Reduce the heat to low, cover, and simmer for 1 hour, or until the lamb is tender and the sauce has thickened. Make sure you stir occasionally, taking care that the spice mixture does not stick to the base of the pan. When the lamb is cooked, sprinkle with the coriander leaves, replace the lid and cook for 5 minutes further. Serve the lamb korma hot with rice. 
\end{enumerate}
