\section{Lasagne}

\index{meat!beef!mince}
\index{starch!pasta}
\index{country!Italy}
\index{source!Clare Richmond}  

The instructions here make a pretty good lasagne, but it seems like one might get better results by making Kenji's ragu bolognese (in this book) and a cheese bechemal on the stovetop.

\subsection{Ingredients}

Meat sauce:

\begin{itemize}
    \item 1 onion
    \item 1 clove garlic
    \item 125g mushrooms
    \item 500g
    \item beef mince
    \item Salt and pepper
    \item \sfrac{1}{2} teaspoon oregano
    \item 1 teaspoon sugar
    \item 2 440g cans tomato puree
\end{itemize}

Cheese sauce:

\begin{itemize}
    \item 60 g butter
    \item 4 tablespoons flour
    \item Salt and pepper
    \item Pinch nutmeg
    \item 2 cups milk
    \item 125g cheddar cheese
    \item 1 tablespoon grated parmesan cheese
\end{itemize}

Assembly:

\begin{itemize}
    \item Oil
    \item Lasagne sheets
    \item 60g cheddar cheese
    \item 2 tbsp grated parmesan cheese
    \item 250g packet frozen spinach (optional)
    \item \sfrac{1}{2} cup cream
\end{itemize}

\subsection{Method}

Meat sauce:

\begin{enumerate}
    \item Peel and finely chop onion, crush garlic, slice mushrooms finely.
    \item Heat the oil in a pan and brown the meat.
    \item Add onion, garlic and mushrooms, cook until onion transparent.
    \item Season with salt and pepper, add oregano, sugar and tomato.
    \item Bring to boil, reduce heat, simmer covered 45 minutes.
    \item Uncover, simmer until sauce is thick (around 15 minutes).
\end{enumerate}

Cheese sauce:

\begin{enumerate}
    \item Melt butter in a microwave proof bowl/jug.
    \item Add flour, salt, pepper, nutmeg, blend until smooth.
    \item Put in microwave for a couple of min on high.
    \item Remove and gradually stir in the milk.
    \item Put in microwave for 2 or 1 minute bursts on high, stirring after each go until the sauce is thick and creamy.
    \item Remove from microwave and stir in the grated cheddar and parmesan until cheeses melt.
\end{enumerate}

Assembly:

\begin{enumerate}
    \item Assemble the lasagne in layers: pasta, meat, cheese sauce
    \item Top with pasta.
    \item Sprinkle top with combined cheeses.
    \item Bake in \celsius{180} oven uncovered 20 minutes.
    \item Drizzle top evenly with cream.
    \item Bake for a further 10 to 15 minutes or until golden brown.
    \item Stand 10 minutes before serving.
\end{enumerate}
