\section{Minestrone Soup}

\index{author!J. Kenji Lopez-Alt}
\index{source!seriouseats.com}
\index{vegetarian}
\index{starch!pasta}
\index{country!Italy}

Source: https://www.seriouseats.com/the-best-minestrone-soup-recipe

\subsection{Ingredients}

\begin{multicols}{2}
    For the stock

    \begin{itemize}
        \item 1 medium onion, split in half
        \item 1 medium carrot
        \item 2 celery stalks
        \item 2 medium cloves garlic
        \item 1 large sprig rosemary
        \item 2 to 3 sprigs parsley
        \item 1 bay leaf
    \end{itemize}

    \vfill\null
    \columnbreak

    For the soup

    \begin{itemize}
        \item 1 medium onion, finely chopped
        \item 1 medium carrot, peeled and finely diced
        \item 2 celery stalks, finely diced
        \item 1 tbsp fresh rosemary leaves, minced
        \item 2 cloves garlic, minced
        \item 1 400g can crushed tomatoes
        \item 1 Parmesan rind (optional)
        \item 1 cup small pasta (e.g. macaroni)
        \item 1 400g can cannellini, borlotti, or kidney beans
        \item 1 medium zucchini, finely diced
        \item 1 medium summer squash, finely diced
        \item 1 bag spinach, roughly chopped
    \end{itemize}
\end{multicols}

\subsection{Method}

\begin{enumerate}
    \item \emph{For the stock:} Combine onion halves, carrot, celery, garlic cloves, rosemary, parsley, and bay leaf in a large pot and cover with water by several inches. Add a pinch of salt. Bring to a boil, reduce to a simmer, and cook, topping up with water as necessary, for about 45-60 minutes. Using tongs, discard vegetables and aromatics. Drain beans, reserving cooking liquid. Transfer bean-cooking liquid to a vessel and add enough cold water to equal 2L.
    \item \emph{For the soup:} Return the empty pot to medium-high and heat oil until just shimmering. Add onion, carrot, celery, and minced rosemary. Season with a big pinch of salt and cook, stirring, until vegetables are softened but not browned, 10 to 15 minutes, adding more oil if pot appears dry or if vegetables are starting to stick to the bottom.
    \item Add garlic and cook, stirring, until fragrant, about 30 seconds. Add tomatoes and cook, stirring, until most of their moisture has evaporated and the mixture starts to fry.
    \item Add reserved bean-cooking liquid, beans, and Parmesan rind, if using. Let broth simmer for at least 10 minutes.
    \item Discard Parmesan rind, if used. Add beans, zucchini, squash, and spinach and simmer for up to 2\sfrac{1}{2} hours. Add the pasta 10-15 minutes before serving.
    \item Stir in chopped herbs and season to taste with salt and pepper before serving.
\end{enumerate}

