\clearpage
\section{One Pot Mexican Chicken}

\index{meat!chicken!thigh}
\index{meat!chicken!breast}
\index{starch!rice}
\index{rice cooker}
\index{quick-n-easy}
\index{author!Kylie Perrotti}

Source: https://www.triedandtruerecipe.com/easy-one-pot-chicken-and-rice/

\subsection{Ingredients}

\begin{itemize}
    \item 1 tbsp neutral oil
    \item 1 onion, diced
    \item 1 jalapeno, minced
    \item 500g chicken thighs, skinless and boneless, cut into bite-sized pieces
    \item 1 tbsp butter
    \item 5 cloves garlic, minced
    \item 1 tbsp Mexican seasoning (see below)
    \item 1 cup medium-grain rice
    \item 2\sfrac{1}{4} cups chicken stock
    \item Salt and pepper, to taste
    \item 1 scallion, sliced thinly, for garnish
    \item Fresh coriander, for garnish
    \item Lime wedges, for serving
    \item 1-2 avocados, for serving
\end{itemize}

\subsection{Mexican Seasoning}

\begin{itemize}
    \item 1 tbsp chili powder
    \item 2 tsp cumin
    \item 1 tsp paprika
    \item \sfrac{1}{2} tsp smoked paprika
    \item cayenne powder, to taste
\end{itemize}

\subsection{Method}

\begin{enumerate}
    \item Heat oil in a large pot over medium-high heat. Add onion and jalapeno and cook until softened, about 5 minutes.
    \item Add chicken and cook until almost cooked through, about 10 minutes.
    \item Push the chicken to the side and add butter, garlic, and Mexican seasoning. Cook for 45 seconds, until fragrant.
    \item Stir to coat the chicken in garlic and seasoning.
    \item Add the rice and mix until everything is evenly distributed.
    \item Season lightly with salt and pepper, then cook for 1-2 minutes to toast the rice.
    \item Add the water and bring to a boil. Reduce heat to low, cover, and simmer for 20-25 minutes.
    \item Turn off the heat and let sit for 5-10 minutes, covered.
    \item Season to taste, then serve.
\end{enumerate}
