\section{Orecchiette With Broccoli and Toasted Hazelnuts}

\index{author!Nik Sharma}
\index{source!seriouseats.com}
\index{vegetarian}
\index{starch!pasta}
\index{country!Italy}

Source: https://www.seriouseats.com/orecchiette-with-broccoli-and-toasted-hazelnuts-recipe-7507873

\subsection{Ingredients}

\begin{itemize}
    \item \sfrac{1}{4} cup extra-virgin olive oil
    \item 680g broccoli (about 2 large heads), florets cut into roughly 1" pieces
    \item 2 cloves garlic, minced
    \item Pinch red pepper flakes
    \item 1 cup heavy cream
    \item \sfrac{1}{2} tsp turmeric
    \item 500g orecchiette pasta
    \item \sfrac{1}{2} cup parmesan cheese, finely grated
    \item \sfrac{1}{2} cup hazelnuts, blanched, toasted, and coarsely chopped
\end{itemize}

\subsection{Method}

\begin{enumerate}
    \item In a medium Dutch oven or large sauté pan, heat oil over high heat until just smoking. Add half the broccoli, season lightly with salt, and cook, stirring occasionally, until well browned on at least one side, about 5 minutes. Lower heat to medium-low, stir in remaining broccoli, and season lightly with salt. Stir in garlic and red pepper flakes and cook until garlic is fragrant, about 30 seconds.
    \item Add heavy cream along with 1 cup water and the turmeric, bring to a simmer over medium-high heat. Cover and cook until broccoli is very tender, about 10 minutes. Remove from heat.
    \item Meanwhile, bring a large pot of salted water to a boil. Add orecchiette and cook until just shy of al dente (1 to 2 minutes fewer than package directions). Drain pasta, reserving \sfrac{1}{2} cup pasta water.
    \item Add orecchiette to pasta sauce and cook over medium-high heat, stirring constantly, until pasta is al dente and sauce is thickened and coats noodles, but is still liquid enough to pool in the bottom of the pot, about 2 minutes. Add more water, in \sfrac{1}{4} cup increments as needed, to achieve desired consistency (keep in mind, it will thicken even more once cheese is stirred in).
    \item Remove from heat, add parmesan, and stir vigorously to incorporate. Season with salt to taste. Divide between warmed serving bowls, topping each portion with toasted hazelnuts and additional grated parmesan. Serve immediately.
\end{enumerate}

