\section{Pasta with Sausage and Broccoli}

\index{author!Sasha Marx}
\index{meat!pork}
\index{meat!pork!sausage}
\index{starch!pasta}
\index{country!Italy}
\index{alcohol!white wine}
\index{quick-n-easy}
\index{source!seriouseats.com}
  
Source: https://www.seriouseats.com/orecchiette-broccoli-rabe-sausage
  
\subsection{Ingredients}
  
\begin{itemize}
  \item Kosher salt
  \item 3 tbsp extra-virgin olive oil
  \item 250g Italian sausage, removed from casing
  \item 3 cloves garlic, minced
  \item 2 anchovy fillets
  \item \sfrac{1}{2} tsp red pepper flakes
  \item \sfrac{1}{2} cup dry white wine
  \item 500g broccolini
  \item 350g pasta (short, e.g. spirali)
  \item 40g grated Pecorino Romano (or Parmesan), plus extra for serving
\end{itemize}

\subsection{Method}

\begin{enumerate}
  \item Bring a large pot of salted water to a boil.
  \item Meanwhile, in a large skillet, heat olive over medium heat until shimmering. Using clean hands, add sausage to skillet by pinching off \sfrac{1}{2}- to \sfrac{3}{4}-inch pieces and arranging in a single layer in the pan. Alternatively, add sausage to skillet all at once, then break up into pieces with a wooden spoon, spreading them out evenly in the pan. Cook over medium heat, undisturbed, until bottom side is light golden brown, about 2 minutes.
  \item Using a spoon or thin metal spatula, turn sausage pieces onto uncooked side. Add garlic, anchovy (if using), and pepper flakes, and continue to cook until fragrant and anchovy has dissolved, 30 seconds to 1 minute.
  \item Increase heat to medium-high and add wine. Bring to a simmer and cook, swirling pan and scraping up any stuck-on bits with a wooden spoon, until wine has emulsified with olive oil and mixture is slightly reduced, about 30 seconds. Turn off heat.
  \item Add broccolini stalk pieces (with florets attached) to boiling water and cook until stalks are barely tender, 1 \sfrac{1}{2} to 2 minutes. Using a spider skimmer, drain well and transfer to a plate. Using a sharp knife, cut stalks and florets into 1 \sfrac{1}{2}-inch pieces. Set aside.
  \item Start cooking pasta. When pasta is 10 minutes from being done, transfer 1 cup of pasta cooking water to skillet along with broccolini; continue cooking pasta. Return skillet to high heat and bring to a boil, swirling and stirring pan constantly until cooking water emulsifies with olive oil mixture, 1 to 2 minutes.
  \item Meanwhile, continue cooking pasta until it is softened on the exterior, but well shy of al dente and still uncooked in the center (about 3 minutes less than the package directions). Drain pasta, making sure to reserve at least 2 cups of the cooking water.
  \item Cook on high heat, stirring and tossing rapidly, until pasta is al dente and sauce is thickened and coats noodles, 2 to 3 minutes, adding more pasta cooking water in \sfrac{1}{4} cup increments as needed.
  \item At this point, the sauce should just pool around the edges of the pan; it will continue to tighten up in the time it takes to plate and serve, so make sure it's a little looser than the ideal serving consistency.
  \item Remove from heat, add grated cheese, and stir rapidly to incorporate. Season with salt to taste.
  \item Serve with additional cheese on top.
\end{enumerate}
