\section{Peanut, Sweet Potato, and Kale Soup}

\index{author!J. Kenji Lopez-Alt}
\index{source!seriouseats.com}
\index{vegetarian}
\index{starch!rice}
\index{country!Thailand}

Source: https://www.seriouseats.com/west-african-inspired-vegan-peanut-sweet-potato-soup-recipe

\subsection{Ingredients}

\begin{itemize}
    \item 6 medium cloves garlic
    \item 1\sfrac{1}{2}" knob of ginger, peeled and roughly chopped
    \item 45g cilantro, thick stems reserved separately from leaves and tender small stems
    \item 1 Serrano or jalapeño chile, stemmed and halved, divided
    \item 2 400ml cans full-fat coconut milk
    \item 2 tbsp vegetable oil, divided
    \item 6 scallions, whites and pale green parts only, thinly sliced, divided
    \item 1 tsp ground turmeric
    \item 1L water or vegetable stock
    \item 250g sweet potatoes, peeled and cut into \sfrac{1}{2}"
    \item \sfrac{1}{3} cup peanut butter
    \item 2 tsp sugar
    \item 140g bunch kale, thick stems discarded, leaves very roughly chopped
    \item 1 tbsp lime juice
    \item Hot sauce, such as Frank's Red Hot, to taste
    \item Rice, for serving (I like using red or black rice)
\end{itemize}

\subsection{Method}

\begin{enumerate}
    \item Combine garlic, ginger, thick cilantro stems, and half of the chile in the bowl of a mortar and pestle (see notes). Sprinkle with about 1 teaspoon of salt. Pound into a rough paste and set aside. Thinly slice remaining half chile and set aside for garnish.
    \item Open 1 can of coconut milk and carefully spoon off about 3 tablespoons of the solid fat from the surface and place it in a large Dutch oven. Add 1 tablespoon of vegetable oil. Heat over medium-high heat, stirring frequently, until coconut fat separates and solids start to sizzle, about 4 minutes. Continue cooking, stirring constantly, until solids turn pale golden brown, about 1 minute longer. Add the pounded garlic/ginger mixture and cook, stirring, until aromatic, about 30 seconds. Add half of sliced scallions and turmeric and cook, stirring, until lightly softened, about 1 minute.
    \item Add remaining contents of both cans of coconut milk along with 1 quart of water or stock. Add sweet potatoes. Bring to a boil, and reduce to a bare simmer. Cook until sweet potatoes are totally softened, about 15 minutes.
    \item Add peanut butter.
    \item When potatoes are fully softened, blend soup until mostly smooth but a little texture remains using a hand blender directly in the pot or by transferring to a countertop blender in batches. Bring to a simmer, stir in kale, and cook until kale is completely wilted and tender, about 5 minutes. Stir in lime juice. Season soup to taste with salt, pepper, and hot sauce. Stir in cilantro, reserving some for garnish. Serve soup with rice, sprinkled with cilantro, chopped peanuts, scallions, and sliced chiles.
\end{enumerate}

\emph{For a risotto-like experience, add 2 (rice) cups of rice to the soup after blending and cook until rice is done.}
