\clearpage
\section{Rice Cooker "Chinese" Chicken}

\index{meat!chicken!thigh}
\index{meat!chicken!breast}
\index{starch!rice}
\index{rice cooker}
\index{quick-n-easy}
\index{author!Jeeca}

Source: https://thefoodietakesflight.com/rice-cooker-meal/

\subsection{Ingredients}

\begin{itemize}
    \item 1 cup sushi rice
    \item 1 cup water (1:1 ratio)
    \item 1 tbsp soy sauce
    \item 1 tbsp dark soy sauce
    \item 1 tbsp sugar
    \item 1 tbsp oyster sauce
    \item 2 tsp sesame oil
    \item 2 cloves garlic, minced
    \item 1 scallion, sliced thinly
    \item \sfrac{1}{2} carrot, 5mm diced
    \item 4 mushrooms, preferably shiitake, sliced
    \item 1 head bok choy, chopped
    \item 2 tbsp edamame, shelled
    \item 1 capsicum, diced
    \item 500g chicken thighs, skinless and boneless, cut into bite-sized pieces
    \item Other vegetables or proteins as you desire.
    \item Sesame seeds, for garnish
    \item Chilli garlic sauce, for serving
\end{itemize}

\subsection{Method}

\begin{enumerate}
    \item Wash rice until water runs clear, then drain and put in the rice cooker.
    \item Add water, soy sauce, dark soy sauce, sugar, oyster sauce, sesame oil, garlic, and scallion. Mix well.
    \item Add carrot, mushrooms, bok choy, edamame, and capsicum on top of the rice.
    \item Add chicken on top of the vegetables.
    \item Close the lid and set the rice cooker to cook.
    \item Once the rice cooker switches to warm, then mix everything together and serve with sesame seeds and chilli garlic sauce.
\end{enumerate}
