\clearpage
\section{Roast Lime Chicken with Sweet Potatoes}

\index{meat!chicken!whole}
\index{starch!sweet potato}
\index{roast}

\subsection{Ingredients}

\begin{itemize}
    \item 2 cloves garlic, minced
    \item 2 cloves garlic, bruised but whole
    \item \sfrac{1}{3} cup coriander, coarsely chopped
    \item 1 tsp ground turmeric
    \item 5cm piece fresh turmeric, coarsely chopped
    \item 1 roasting chicken (~1.5kg), butterflied
    \item 1 lime, halved
    \item 4 sweet potatoes, peeled and cut into wedges
    \item 300mL chicken stock
    \item 2 tbsp soy sauce
\end{itemize}

\subsection{Method}

\begin{enumerate}
    \item Calculate cooking time for the chicken: 20 minutes per 500g, plus 20 minutes.
    \item Preheat the oven to \celsius{190}.
    \item Grind the minced garlic, coriander, 2 tsp salt, ground turmeric, and fresh turmeric into a paste (use a mortar and pestle or a food processor).
    \item Place chicken skin-side up in a roasting pan. Using a spoon, separate the skin from the meat but leave it attached. Spoon the paste under the skin, smooshing it around for even coverage.
    \item Squeeze the limes over the chicken, then place them underneath the chicken along with the whole cloves of garlic.
    \item Cover with foil and put in the oven.
    \item Meanwhile, bring a pot of water to a boil. Add the sweet potatoes and cook until just barely tender (about 10-15 minutes).
    \item Drain the potatoes and place them around the chicken in the roasting pan. Baste with the juices from the pan and sprinkle with salt and pepper. Cover again and return to the oven.
    \item About 20 minutes before the end, remove the foil and baste the chicken with juices from the pan. Turn the sweet potatoes over. Return to oven and continue to cook, uncovered.
    \item When the chicken is done, drain it of any juices and remove it to a carving board. Cover loosely with foil and let it rest.
    \item Transfer the sweet potatoes to a serving dish and keep warm.
    \item Skim off the oil from the roasting pan but keep the juices. Over medium heat, bring the juices to a boil, then pour in the stock.
    \item Stirring constantly, bring to a boil and scrape up any fond that formed. Stir in the soy sauce and check seasoning before straining into a serving vessel.
    \item Carve chicken and serve with the sweet potatoes and gravy.
\end{enumerate}
