\section{Somali-style Biryani}

\index{starch!rice}
\index{starch!rice}
\index{meat!chicken!thigh}
\index{source!goonswithspoons.com}
\index{country!Somalia}

From \detokenize{http://goonswithspoons.com/Somali-Style_Bryiani_Rice}

\subsection{Ingredients}

\begin{itemize}
    \item 500g chicken thighs
    \item \sfrac{1}{2} tsp ginger, grated
    \item Fresh mint, de-stalked
    \item Mozzarella cheese, grated
    \item 1 large onion, roughly chopped
    \item 4 cloves garlic, grated
    \item Fresh coriander, minced
    \item 1 tsp chicken stock powder (or 1 cube)
    \item \sfrac{1}{2} tsp ground cumin
    \item 3 cups Basmati rice, washed
    \item 2 large carrots, julienned
    \item 2 large potatoes, julienned
    \item Raisins
    \item Pine nuts
\end{itemize}

\subsection{Method}

\begin{enumerate}
    \item In a large pot, brown the chicken for 2 minutes, then add the yoghurt, ginger, and mint, lower heat to a simmer and cook uncovered for 40 minutes, until chicken is tender.
    \item Fish out the chicken pieces and place them in an oiled roasting pan.
    \item Strain the liquid and reserve for use later. Place the yoghurt/mint solids on top of the chicken.
    \item Put the chicken in a \celsius{180} oven for 10 minutes, then top with mozzarella and return to the oven for another 2 minutes.
    \item In the same pot as the chicken was cooked in, on low heat, saute the onion until it's just starting the soften. Add the garlic, coriander, stock powder, and spices and cook for another minute, then add the rice and stir to coat.
    \item Add the liquid from earlier, covering the rice, and let cook until the rice is done.
    \item In a frying pan over medium-high heat, shallow fry the carrots and potatoes, then remove to a plate and empty out the oil.
    \item Saute the raisins for 90 seconds, then add the pine nuts for another 30 seconds, then turn off the heat and return the carrot and potato to the pan.
    \item Plate the rice and chicken, top the rice with the carrot mixture, and serve.
\end{enumerate}