\clearpage
\section{Sweet Potato Soup}

\index{author!Nagi Maehashi}
\index{source!recipetineats.com}
\index{vegetarian}

Source: https://www.recipetineats.com/sweet-potato-soup

\subsection{Ingredients}

\begin{itemize}
    \item 2 tbsp extra virgin olive oil
    \item 2 tbsp unsalted butter
    \item 2 onions, diced
    \item 2 leeks, white and pale green part only, quartered, cut into 1cm slices
    \item 2 garlic cloves, minced
    \item 1 kg sweet potato, peeled, quartered lengthwise, cut into 2cm chunks
    \item 1 tbsp cumin powder
    \item 1\sfrac{1}{4}L vegetable stock
    \item 1\sfrac{1}{2} tsp salt
    \item 1 tsp black pepper
    \item \sfrac{1}{3} cup cream
\end{itemize}

For garnishing:

\begin{itemize}
    \item Something to drizzle/dollop: extra virgin olive oil, cream, yogurt, sour cream
    \item Something crunchy: flatbread strips, croutons, pistachios, pepitas, crispy fried shallots
\end{itemize}

\subsection{Method}

\begin{enumerate}
    \item Heat the oil and butter in a large heavy based pot over medium heat. Cook the onion, leek, and garlic for 5 minutes until softened.
    \item Add the sweet potato and cumin, cook for another 3 minutes, stirring regularly.
    \item Add the stock, salt, and pepper. Bring to a simmer, then cook for 20 minutes at a gentle simmer until the sweet potato is very tender (no lid).
    \item Remove the pot from the stove and blitz with a hand-held stick until smooth. Stir in cream.
    \item Ladle into bowls and add garnishes.
\end{enumerate}
