\section{Vegan bolognese}

\index{starch!pasta}
\index{vegetarian}
\index{vegan}
\index{dairy-free}
\index{gluten free}
\index{source!sweetpeasandsaffron.com}
\index{author!Denise Bustard}


From https://sweetpeasandsaffron.com/vegan-bolognese

\subsection{Ingredients}

\begin{itemize}
	\item 1 onion, peeled and cut into eighths
    \item 250g mushrooms, washed, trimmed, and quartered
    \item 1 cup walnut pieces
    \item 2 carrots, cut into chunks
    \item 2 ribs celery, cut into chunks
    \item \sfrac{1}{4} cup olive oil
    \item 4 cloves garlic, minced
    \item \sfrac{1}{4} cup white wine
    \item 2 400g cans crushed tomatoes
    \item 1\sfrac{1}{2} tsp salt
    \item \sfrac{1}{2} tsp nutmeg
    \item 1 bay leaf
    \item \sfrac{2}{3} cup red lentils
    \item 2 cups vegetable stock
    \item \sfrac{1}{2} cup nutritional yeast
    \item 1 tbsp balsamic vinegar
    \item Pasta, for serving
\end{itemize}

\subsection{Method}

\begin{enumerate}
    \item In a food processor fitted with a steel blade, add the mushrooms and onions. Process, until chopped into very small pieces, scraping down sides as needed.
    \item Add the walnuts to the processor with the onions and mushrooms and pulse 10-15 times, until chopped into very small pieces.
    \item Transfer the mixture to a clean bowl. In the food processor, add the carrot and celery. Process until chopped in very small pieces, then set aside.
    \item In a pot, heat the olive oil over medium heat. Add the onion/mushroom/walnut mixture and cook, stirring frequently, until the mixture has steamed off most of the liquid and begins to brown. Keep an eye that it doesn't burn.
    \item Make a space in the middle of the pot and add the garlic. Cook for 1 minute.
    \item Add the white wine and simmer for 2-3 minutes, scraping the bottom of the pot with a spatula to remove all brown bits.
    \item Add the carrot/celery mixture, crushed tomatoes, salt, nutmeg, bay leaf, lentils, and stock.
    \item Cover and simmer for 45 minutes, or until lentils are done to your liking. Stir the pot occasionally and keep an eye on the temperature so it doesn't stick to the bottom of the pot and burn.
    \item Stir in the nutritional yeast and balsamic vinegar, taste and adjust seasoning, and serve!
\end{enumerate}
