\section{Sausage McMuffins}

\index{starch!bread}
\index{author!Nagi Maehashi}
\index{country!America}

From: https://www.recipetineats.com/homemade-sausage-egg-mcmuffin/

\subsection{Ingredients}

\begin{itemize}
	\item 500g pork or beef mince
	\item \sfrac{1}{2} tsp dried ground sage
	\item \sfrac{1}{2} tsp dried thyme
	\item 1 tsp onion powder or garlic powder
	\item \sfrac{3}{4} tsp black pepper
	\item \sfrac{3}{4} tsp salt
	\item \sfrac{1}{2} tsp sugar
	\item 2 tbsp oil
	\item 4 eggs
	\item 4 English muffins, cut in half
	\item 4 slices processed cheese
	\item 4 rashers bacon (optional)
\end{itemize}

The meat used in McDonald's sausage patties differs around the world! Pork is used in the US and Canada, and beef is used in Australia. Pork is juicier and patties are more tender so reheats better.

\subsection{Method}

\begin{enumerate}
	\item Preheat oven to \celsius{130}.
	\item Place muffins on a baking tray, cut side up, and top with cheese. Put them in the oven until they crisp \emph{just slightly}.
	\item Mix Sausage Patty ingredients in a bowl. Shape into 4 thick or 5 "authentic"-sized patties. Make them slightly oversized because they will shrink.
	\item Heat oil over high heat in two non-stick pans.
	\item Add the patties to one pan and cook until the first side is browned. Flip and cook until the second side is also browned.
	\item Meanwhile, crack the eggs into rings in the second pan. Add 2 tbsp water to the pan and cover for 1-2 minutes or until eggs are done to your liking.
	\item Stack muffin bottom, sausage, egg, then muffin top.
\end{enumerate}
